Dynamic Topic Modeling for Voice Dialogues

### 2024-05-23 paper/main.tex
update lib

The dialogue segmentation stage represents the initial stage for textual type of data. 
The result is a set of utterance indices that indicate the beginning of a thematically related group.

@@

In order to indicate the thematic similarity of two statements in a dialogue, the $[CLS]$ token is employed, which performs a similar role in the usual BERT. 
The resulting value is subjected to a linear dictionary and a final similarity value is obtained, which is then utilised to calculate Coherence scores.

@@

The greater the depth score between two statements, the less likely it is that they share a thematic relationship. 
To identify the pairs along which the boundaries of the thematic segments lie, the threshold value is calculated as follows: $threshold = \mu - \frac{\sigma}{2}$, where $\mu$ is the average value and $\sigma$ is the standard deviation. Pairs with a depth score above the $threshold$ value will be choosen as boundaries.

@@

As for the quality evaluation of the extracted topics, we will use two metrics: Topic coherence and Topic diversity
\begin{itemize}
    \item \textbf{Topic diversity} \cite{topicdiversity:2019} is a metric that assesses the ratio of unique keywords across all topic representations. This metric is used to measure the capabilities of a topic model covering a wide range of topics. The diversity score is a value between 0 and 1, with a score of 0 indicating repetitive topics and a score of 1 indicating diverse topics.
    \item \textbf{Topic coherence} \cite{topiccoh:2009} is a measure of the degree of interconnection of words within a topic. In our experiments, we employed normalized point-to-point mutual information (PMI) as a metric for thematic consistency. A higher score for a given name indicates greater consistency, with an absolute correlation estimated at 1 point.
\end{itemize}

@@

The pipeline of dynamic thematic modelling of audio dialogues, which will be considered in this paper, is divided into several main stages. 
These include ASR, dialogue segmentation, topic extraction and topic evolution.

@@

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \cline{2-7}
         & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        GraphSeg & 0.462 & 0.466 & 0.239 & 0.496 & 0.515 & 0.238 \\
        TextTilling & 0.469 & 0.488 & 0.204 & \cellcolor{green!20} 0.446 & \cellcolor{green!20} 0.458 & \cellcolor{green!20} 0.378 \\
        TeT + BERT & \cellcolor{green!20} 0.425 & \cellcolor{green!20} 0.439 & \cellcolor{green!20} 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline\ 
        CohScoring+BERT-NSP & 0.4465 & 0.4575 & 0.267 & 0.5071 & 0.5219 & 0.205 \\ 
        CohScoring+BERT-NSP fine-tune & \cellcolor{green!40} 0.3981 & \cellcolor{green!40} 0.4018 & \cellcolor{green!40} 0.32 & \cellcolor{green!40} 0.4361 & \cellcolor{green!40} 0.44510 & \cellcolor{green!40} 0.285 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{AMI} & \multicolumn{3}{| c |}{ICSI} \\
        \cline{2-7}
        & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.885 & 0.792 & 0.3641 & 0.762 & 0.730 & 0.309 \\
        GraphSeg & 0.875 & 0.750 & 0.422 & 0.810 & 0.756 & 0.275 \\
        TextTilling & Pk & wd & f1 & Pk & wd & f1 \\
        TeT + BERT & Pk & wd & 0.443 & Pk & wd & 0.158 \\ 
        \hline
        CohScoring+BERT-NSP & \cellcolor{green!20} 0.6447 & \cellcolor{green!20} 0.7394 & \cellcolor{green!20} 0.551 & \cellcolor{green!20} 0.6148 & \cellcolor{green!20} 0.6731 & \cellcolor{green!20} 0.779 \\ 
        CohScoring+BERT-NSP fine-tune & \cellcolor{green!40} 0.5854 & \cellcolor{green!40} 0.6032 & \cellcolor{green!40} 0.587 & \cellcolor{green!40} 0.5842 & \cellcolor{green!40} 0.5932 & \cellcolor{green!40} 0.815 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Dialogue segmentation experiments}
\end{center}

@@

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multirow{2}{*}{models} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \cline{2-5}
         & TD & TC & TD & TC  \\ 
        \hline
        LSA  & 0.25824 & 0.00951 & 0.420026 & -0.01929 \\
        BertTopic & 0.34823 & \cellcolor{green!60} 0.02751 & 0.420026 & \cellcolor{green!60} 0.01929 \\
        \hline
        LLaMA3 8B & \cellcolor{green!60} 0.80707 & \cellcolor{green!20} 0.01621 & \cellcolor{green!60} 0.49525 & \cellcolor{green!20} 0.005887 \\ 
        Qwen1.5 7B & \cellcolor{green!20} 0.72169  & 0.015453 & \cellcolor{green!20} 0.47777  & -0.07682\\ 
        Mistral 7B & 0.63344 & 0.002248 & 0.34215 & -0.01689 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{2}{| c |}{AMI} &  \multicolumn{2}{| c |}{ICSI} \\
        \cline{2-5}
         & TD & TC & TD & TC  \\ 
        \hline
        LSA & 0.009648 & 0.001375 & 0.013490 & -0.00172 \\ 
        BertTopic & 0.013996 & \cellcolor{green!60} 0.02485 & 0.029090 & \cellcolor{green!60} 0.27210 \\ 
        \hline
        LLaMA3 8B & \cellcolor{green!60} 0.50863 & \cellcolor{green!20} 0.11409 & \cellcolor{green!60} 0.76137 & \cellcolor{green!20} 0.14734 \\ 
        Qwen1.5  & \cellcolor{green!20} 0.38641 & 0.10328 & \cellcolor{green!20} 0.7185  & 0.00237\\ 
        Mistral 7B & 0.29852 & 0.084103 & 0.5761 & -0.11318 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Dialogue topics extraction experiments}
\end{center}

@@

Summarizing all the results of the article:
\begin{itemize}
    \item Suitable datasets were selected, experiments were carried out on them at all stages and quality metrics of the selected algorithms were obtained;
    \item Among the available solutions, the best available metrics were selected. Experiments were carried out with each of the algorithms at each stage on ready-made models, pre-trained and trained from scratch. The best models were added to the final pipeline;;
    \item At the topic extraction stage, a study was conducted on the use of LLM. The best open-source LLMs were selected for experiments with zero-shot, feat-shot and fine-tuning. The generative approach using LLM shows the results of the best available extractive solutions for topic modeling;
    \item A suitable set of metrics was identified and selected to evaluate the quality of each stage. In order to utilise the metrics, a library with an implementation was Investigated and integrated into pipeline.
\end{itemize}

\putbibliography
\end{document}

>>>>

The dialogue segmentation stage represents the initial stage for textual type of data. 
The result is a set of utterance indices that indicate the beginning of a topicaly related group.

@@

In order to indicate the topic similarity of two statements in a dialogue, the $[CLS]$ token is employed, which performs a similar role in the usual BERT. 
The resulting value is subjected to a linear dictionary and a final similarity value is obtained, which is then utilised to calculate Coherence scores.

@@

The greater the depth score between two statements, the less likely it is that they share a topic relationship. 
To identify the pairs along which the boundaries of the topic segments lie, the threshold value is calculated as follows: $threshold = \mu - \frac{\sigma}{2}$, where $\mu$ is the average value and $\sigma$ is the standard deviation. Pairs with a depth score above the $threshold$ value will be choosen as boundaries.

@@

As for the quality evaluation of the extracted topics, we will use two metrics: Topic coherence and Topic diversity
\begin{itemize}
    \item \textbf{Topic diversity} \cite{topicdiversity:2019} is a metric that assesses the ratio of unique keywords across all topic representations. This metric is used to measure the capabilities of a topic model covering a wide range of topics. The diversity score is a value between 0 and 1, with a score of 0 indicating repetitive topics and a score of 1 indicating diverse topics.
    \item \textbf{Topic coherence} \cite{topiccoh:2009} is a measure of the degree of interconnection of words within a topic. In our experiments, we employed normalized point-to-point mutual information (PMI) as a metric for topic consistency. A higher score for a given name indicates greater consistency, with an absolute correlation estimated at 1 point.
\end{itemize}

@@

The pipeline of dynamic topic modelling of audio dialogues, which will be considered in this paper, is divided into several main stages. 
These include ASR, dialogue segmentation, topic extraction and topic evolution.

@@

The main stage to be investigated is topic extraction. 
The use of LLM (generative approach) for topic modeling began to be investigated quite recently. 
For audio dialogues, which are quite different from text ones, it was not used at all.

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \cline{2-7}
         & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        GraphSeg & 0.462 & 0.466 & 0.239 & 0.496 & 0.515 & 0.238 \\
        TextTilling & 0.469 & 0.488 & 0.204 & \cellcolor{green!20} 0.446 & \cellcolor{green!20} 0.458 & \cellcolor{green!20} 0.378 \\
        TeT + BERT & \cellcolor{green!20} 0.425 & \cellcolor{green!20} 0.439 & \cellcolor{green!20} 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline\ 
        Our method & 0.4465 & 0.4575 & 0.367 & 0.5071 & 0.5219 & 0.430 \\ 
        Our method + fine-tune & \cellcolor{green!40} 0.4094 & \cellcolor{green!40} 0.4048 & \cellcolor{green!40} 0.7374 & \cellcolor{green!40} 0.4361 & \cellcolor{green!40} 0.44510 & \cellcolor{green!40} 0.7421 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{AMI} & \multicolumn{3}{| c |}{ICSI} \\
        \cline{2-7}
        & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.885 & 0.792 & 0.3641 & 0.762 & 0.730 & 0.309 \\
        GraphSeg & 0.875 & 0.750 & 0.422 & 0.810 & 0.756 & 0.275 \\
        TextTilling & Pk & wd & f1 & Pk & wd & f1 \\
        TeT + BERT & Pk & wd & 0.443 & Pk & wd & 0.158 \\ 
        \hline
        Our method & \cellcolor{green!20} 0.6447 & \cellcolor{green!20} 0.7394 & \cellcolor{green!20} 0.551 & \cellcolor{green!20} 0.6148 & \cellcolor{green!20} 0.6731 & \cellcolor{green!20} 0.779 \\ 
        Our method + fine-tune & \cellcolor{green!40} 0.5279 & \cellcolor{green!40} 0.6932 & \cellcolor{green!40} 0.610 & \cellcolor{green!40} 0.5842 & \cellcolor{green!40} 0.5932 & \cellcolor{green!40} 0.815 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Dialogue segmentation experiments}
\end{center}

@@

At this stage, we conducted the most experiments, ready-made solutions were used or adapted for all stages, at the topic extraction stage we used LLM without relying on ready-made solutions.

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | } 
        \hline
        \multirow{2}{*}{models} & \multicolumn{2}{| c |}{Tiage} &  \multicolumn{2}{| c |}{SuperDialseg}  \\
        \cline{2-5}
         & TD & TC & TD & TC  \\ 
        \hline
        LSA  & 0.25824 & 0.00951 & 0.420026 & -0.01929 \\
        BertTopic & 0.34823 & \cellcolor{green!60} 0.02751 & 0.420026 & \cellcolor{green!60} 0.01929 \\
        \hline
        LLaMA3 8B & \cellcolor{green!60} 0.80707 & \cellcolor{green!20} 0.01621 & \cellcolor{green!60} 0.49525 & \cellcolor{green!20} 0.005887 \\ 
        Qwen1.5 7B & \cellcolor{green!20} 0.72169  & 0.015453 & \cellcolor{green!20} 0.47777  & -0.07682\\ 
        Mistral 7B & 0.63344 & 0.002248 & 0.34215 & -0.01689 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{2}{| c |}{AMI} &  \multicolumn{2}{| c |}{ICSI} \\
        \cline{2-5}
         & TD & TC & TD & TC  \\ 
        \hline
        LSA & 0.009648 & 0.001375 & 0.013490 & -0.00172 \\ 
        BertTopic & 0.013996 & \cellcolor{green!60} 0.02485 & 0.029090 & \cellcolor{green!60} 0.27210 \\ 
        \hline
        LLaMA3 8B & \cellcolor{green!60} 0.50863 & \cellcolor{green!20} 0.01140 & \cellcolor{green!60} 0.76137 & \cellcolor{green!20} 0.14734 \\ 
        Qwen1.5  & \cellcolor{green!20} 0.38641 & 0.01032 & \cellcolor{green!20} 0.7185  & 0.00237\\ 
        Mistral 7B & 0.29852 & 0.00841 & 0.5761 & -0.11318 \\ 
        \hline
    \end{tabular}
    \label{table:topicextr}
    \captionof{table}{Dialogue topics extraction experiments}
\end{center}

@@

Summarizing all the results of the article:
\begin{itemize}
    \item Suitable datasets were selected, experiments were carried out on them at all stages and quality metrics of the selected algorithms were obtained;
    \item Among the available solutions, the best available metrics were selected. Experiments were carried out with each of the algorithms at each stage on ready-made models, pre-trained and trained from scratch. The best models were added to the final pipeline;
    \item At the topic extraction stage, a study was conducted on the use of LLM. The best open-source LLMs were selected for experiments with zero-shot, feat-shot and fine-tuning. Using LLM at this stage, it was possible to increase the metrics for audio dialogues. \\
     - Topic Diversity was increased around 10 times, and Topic Coherence is about the same value compared to BertTopic and LSA as shown in \ref{table:topicextr}; \\
     - As for the textual dialogues worth noting that the increase ща Topic Deversity is less and on Topic Coherence BertTopic sometimes shown higher results.
\end{itemize}

\putbibliography
\nocite{hydro:2023}
\nocite{sesseg:2016}
\nocite{todbert:2020}
\nocite{topaware:2020}
\nocite{Plaquet23:2023}
\nocite{dialsystem:2018}
\nocite{jointmdl:2020}
\nocite{clusterllm:2023}
\nocite{atnm:2023}
\nocite{plsa:2013}

\end{document}
